### 2016-07-22 doc/publications/plos16/plos16.tex
edits to page dimensions and marginpar
move description of DT, aded discussion of Strobl

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

@@

@@

\subsection*{RF}

@@

The results are combined in an appropriate way, i.e. for a regression problem,
\begin{equation*}
{\bar {h}}={\frac {1}{B}}\sum _{b=1}^{B} h(x;\theta_b).
\end{equation*}
%where $x$ is the covariate vector of length $p$
%with associated random vector $X$ and the $\theta_b$ are i.i.d. random vectors.

@@

% We also investigated classifying the samples using Random Forests.  We chose random forests due to its ability to
% capture complex interactions between features. Also, due to it being an ensemble method where trees can be formed
% independently, which, is ideal for parallelisation. Furthermore, the ensemble of weak learners can help to minimise
% overfitting and variance.
Decision trees have a number of desirable features, they:
\begin{itemize}
  \item are scale invariant;
  \item can handle categorical and real valued inputs;
  \item can handle missing values;
  \item are insensitive to useless predictors;
  \item are able to capture interactions between features (which is of importance for modelling complex polygenic diseases).
  \end{itemize}
However, the tree fitting algorithm is greedy and may generate an unstable model. That is, a small change in the data may
lead to a very different model. 
\marginpar{a potential problem  with tree models is the tendencey to split on categorical variables with a high number of
  levels, even when better splits are available}
Random forests are a variance reduction technique. They take a tree models which have a low bias but a high variance and
by combining them reduce the variance. The prediction error is the sum of the variance and the bias squared.

@@

>>>>

\documentclass[10pt,a4paper]{article}  %\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

@@

%%local edits (rob)
\let\oldmarginpar\marginpar
\renewcommand\marginpar[1]{\-\oldmarginpar[\raggedleft\footnotesize #1]%hv
{\raggedright\footnotesize #1}}
\reversemarginpar
\setlength{\marginparwidth}{5cm}

@@

Decision trees have a number of desirable features, they:
\begin{itemize}
  \item are scale invariant;
  \item can handle categorical and real valued inputs;
  \item can handle missing values;
  \item are insensitive to useless predictors;
  \item are able to capture interactions between features (which is of importance for modelling complex polygenic diseases).
  \end{itemize}
However, the tree fitting algorithm is greedy and may generate an unstable model. That is, a small change in the data may
lead to a very different model. 
\marginpar{a potential problem  with tree models is the tendencey to split on categorical variables with a high number of
  levels, even when better splits are available}
\subsection*{RF}

@@

The results are combined in an appropriate way, i.e. for a regression problem,
\begin{equation*}
{\bar {h}}={\frac {1}{B}}\sum _{b=1}^{B} h(x;\theta_b).
\end{equation*}
\marginpar{make it a classification example}
%where $x$ is the covariate vector of length $p$
%with associated random vector $X$ and the $\theta_b$ are i.i.d. random vectors.

@@

% We also investigated classifying the samples using Random Forests.  We chose random forests due to its ability to
% capture complex interactions between features. Also, due to it being an ensemble method where trees can be formed
% independently, which, is ideal for parallelisation. Furthermore, the ensemble of weak learners can help to minimise
% overfitting and variance.

Random forests are a variance reduction technique. They take a tree models which have a low bias but a high variance and
by combining them reduce the variance. The prediction error is the sum of the variance and the bias squared.

@@

\cite{Strobl.et.al.2007} demosnstrate that a RF algorithm is subject to a bias in variable selection via two mechanisms:
\begin{itemize}
\item variable scale (for $X_I$ continuous) and number of levels (for $X_i$ discrete) inroduces a bias
\item boosting introduces a bias.
\end{itemize}
These effects will be apparent in the CF algorithm as well. \marginpar{we can fix the boosting effect}
However, there are many examples, (particularly in genomics) whre we have data sets that are
\begin{itemize}
\item very wide
\item all variables have the same number of levels (measures at different points along the genome)
\item the hypothesied functional relationship is of a form amenable to a DT.
\end{itemize}
